### 2021-02-05 introduction.tex
Missing

Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices. Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased \cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}. Security issues in Android software applications (``apps'' for short) have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify source and sink paths involving sensitive data~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}. Using a different approach, researchers have also explored the use of dynamic analysis to mine Android sandboxes, whose goal is to protect Android users from malicious behavior~\cite{DBLP:conf/icse/JamrozikSZ16}.

The main idea of mining sandboxes is to explore the set of calls to sensitive API methods, using different approaches for automatically testing Android apps. These tools, explore apps behavior and record all calls to sensitive APIs. A sandbox builds upon the calls to sensitive Android APIs, during the execution of the test cases (exploratory phase). The sandbox could then block future calls to other sensitive resources which diverge from those found in the exploratory phase. Using this approach, the sandbox accuracy depends on the exploratory capabilities of each testing tool used to mine the sandbox rules.

Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis. The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often assume that additional behaviors are possible than actually would be. Otherwise, static analysis might determine that some behavior is impossible, this behavior no longer needs to be checked at runtime. Thereby, code that is interpreted, decrypted, or downloaded at run time is challenging for static analysis---even though these more \emph{dynamic} strategies are often used to introduce malicious behavior. Nonetheless, the authors do not give any empirical validation about the limitations of static analysis to mine sandboxes. In addition, it is not clear how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.

The same lack of understanding about the role of static analysis also appears in the work of Bao et al. \cite{DBLP:conf/wcre/BaoLL18}, which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes. Their study leverages DroidFax \cite{DBLP:conf/icsm/CaiR17a} to instrument 102 pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
Although the authors report a performance of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore that DroidFax statically analyzes the Android apps and records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.

@@

\todo[inline]{RB.: Later we can enumerate the paper contributions here.}

>>>>

Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices\kn{citation for android being the most popular?}. Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}. Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify source and sink paths involving sensitive data~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} \kn{source and sink arrives out of nowhere in introduction. Either rephrase into a simpler term please or define those in a sentenc before.} and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}. Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes~ \kn{A small sentence defining sandboxes}, whose goal is to protect Android users from malicious behavior~\cite{DBLP:conf/icse/JamrozikSZ16}.

The main idea of mining sandboxes is to explore the set of calls to sensitive API methods \kn{in an Android app?}, using different approaches for automatically testing Android apps. These tools \kn{these analysis? because tools was not a word used before}, explore apps behavior and record all calls to sensitive APIs. A sandbox builds upon the calls to sensitive Android APIs, during the execution of the test cases (exploratory phase). The sandbox could then block future calls to other sensitive resources which diverge from those found in the exploratory phase. Using this approach, the sandbox accuracy depends on the exploratory capabilities of each testing tool used to mine the sandbox rules. \kn{This paragraph attempts to explain what a sandbox does and what it is dependent on, but the overall picture is still not clear. Consider defining sandbox in one sentence in previous paragraph, and in this paragraph use more concise terms like "Given an App A, with sensitive calls Set\_s, a Sanxbox Y does .....}

Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis. The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often assume that additional behaviors are possible than actually would be \kn{Ok. In the first paragraph we discuss static analysis in general to detect vulnerabilities and now without mentioning it prior we seem to mention static analysis can also mine sandboxes. The overall flow of definitions needs some thought}. Otherwise, static analysis might determine that some behavior is impossible and therefore no longer needs to be checked at runtime. Thereby, code that is interpreted, decrypted, or downloaded at run time is out of scope for static analysis---even though these more \emph{dynamic} strategies are often used to introduce malicious behavior. Nonetheless, the authors do not give any empirical validation about the limitations of static analysis to mine sandboxes. As a consequence, it is not clear whether and how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.

The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18}, which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes. Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
Although the authors report a performance kn{performance or accuracy/ precision?} of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.

@@

\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
\kn{The rest of the paper is organized as follows...}
